---
title: "Jessica Bernardin"
output: 
   flexdashboard::flex_dashboard:
    css: flexstyles.css
    social: [ "twitter", "github" ]
    source_code: "https://github.com/jessibernardin/jessibernardin.github.io.git"
    theme: yeti
    logo: ./img/pitcherplant.png
---

```{r setup, include=FALSE}
suppressPackageStartupMessages({
  library(flexdashboard);
  library(sf);
  library(leaflet);
  library(here);
  library(viridis);
  library(mapview);
  library(plotly)
})
knitr::opts_chunk$set(echo = FALSE, warning=FALSE)
knitr::opts_knit$set(root.dir = normalizePath("../"))
htmltools::tagList(rmarkdown::html_dependency_font_awesome())
```

Research {.storyboard data-icon="fa-leaf"}
=========================================

### Dissertation Research  {data-commentary-width=400}

```{r, out.width = '100%'}
#knitr::include_graphics(paste0(here(),"/img/pictureofsarracenia"))
```

***

#### **BACKGROUND**

 - background
    - **bold**
    - **bold**

#### **KEY QUESTIONS**

 1. 
 

### Microbial function and host health {data-commentary-width=400}


```{r m1, out.width = '75%', echo=F, warning=F, message=F}
suppressPackageStartupMessages({
  #library(leaflet);
  library(tidyverse);
  library(sf);
  library(mapview);
  library(shiny);
  library(plotly)
})  

```

*** 

### Effect of environmental extremes on microbial function.

 - 


### Effect of altitude and successtion on microbial function.



***


### Effect of prey type on microbial function



Community {.storyboard data-icon="fa-globe"}
=========================================

### Sustainability Council

### Planting Science Liason and Mentor  {data-commentary-width=400}

### Undergraduate Mentorship

```{r, out.width = '100%'}
#knitr::include_graphics(paste0(here(),"/img/pic"))
```

***

#### details

 - 
 - 
 - 
 

Media {data-icon="fa-television"}
=========================================

#### video title

<iframe width="560" height="315" src="https://www.youtube.com/embed/0-AWqzzeRBM" title="YouTube video player" frameborder="0" allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture" allowfullscreen></iframe>




Photos {data-icon="fa-camera-retro"}
=========================================

Column {data-width=600}
-----------------------------------------------------------------------

<br>

#### **Title**

> *"Quote”* - author
```{r out.height= '60%', fig.align='center'}
#knitr::include_graphics(paste0(here(),"/img/image"))
```
